Timeliness of security updates for Android

### 2014-10-27 securityupdates.tex
Write a subsection on incentives

\subsection{Incentives and participants}
\label{sec:economics}
\todo{write this}

>>>>

\subsection{Incentives and participants}
\label{sec:economics}
Google and other Android vendors care about the reputation of Android, particularly from a security standpoint as if users are afraid to use their devices for certain purposes (e.g.\ banking) then they will not be willing to pay as much for them and money cannot be made from those activities.
Manufacturers make money by selling the device, once sold they want to prevent the cost of return under warranty and so are adverse to the risk of breaking the device, but they do not need to do things to make the device better as it has already been sold.
However if they gain a reputation for abandoning devices that might decrease future sales.

Operators sell phones under contracts, typically at least a year long, they want the user to not request support due to the device breaking.
They might also gain advantage if the user is happy with the device after the end of the contract as they might then keep paying the same rate but there would no longer be a capital cost to pay off.
They care about phones not getting malware which causes support requests or uses the mobile network to perform malicious actions as they may have to reimburse the cost of premium SMS's if they were not authorised by the user.

Users want to buy phones which will serve their use cases and which are secure so that they do not experience negative consequences.
